A Survey of Near-Term Exoskeleton Technology\\ (Draft 3.0)

### 2015-09-29 technology.tex
more updates

Can we expect major improvements in hydraulics?
There has been incremental improvement on HPUs and valves since
the 1950s. Rapid prototyping and 3D printing are leading to
easier integration of valves, actuators, and sensors (see following
paragraph). Current high performance valves are flow control valves. It
is possible that lower leakage valves could be developed. It is possible
that pressure control valves would reduce the need for high bandwidth
force control, and thus high bandwidth valves. Pressure control valves
could also greatly improve exoskeleton safety if pressure control was
implemented physically rather than computationally, since physical
mechanisms are less likely to ``go unstable''.
Bypass mechanisms (a form of clutch) would allow hydraulic systems
to be backdriven without oil flow at high force, which would reduce
the power load on the HPU and the need for high performance force control.
Any valves or additional hydraulic circuitry
would have to have low internal leakage, and previous attempts at
pressure control valves have had leakage problems.
Gear shifts and variable transmissions would allow the maximum torque
and maximum no-load speed of the joint to be increased (also true
for all other actuation types).

@@

>>>>

Can we expect major improvements in hydraulics?
There has been incremental improvement on HPUs and valves since
the 1950s. Rapid prototyping and 3D printing are leading to
easier integration of valves, actuators, and sensors (see following
paragraph). Current high performance valves are flow control valves. It
is possible that lower leakage valves could be developed. It is possible
that pressure control valves would reduce the need for high bandwidth
force control, and thus high bandwidth valves. Pressure control valves
could also greatly improve exoskeleton safety if pressure control was
implemented physically rather than computationally, since physical
mechanisms are less likely to ``go unstable''.
Bypass mechanisms (a form of clutch) would allow hydraulic systems
to be backdriven without oil flow at high force, which would reduce
the power load on the HPU and the need for high performance force control.
Any valves or additional hydraulic circuitry
would have to have low internal leakage, and previous attempts at
pressure control valves have had leakage problems.
It is possible that operating at higher pressures would lead to improved
system performance.

@@

Simple attachements of a linear actuator to a rotary joint lead to
a sinusoidal dependence of the moment arm on the joint angle.
The moment arm can be made more constant or programmed with
a different dependence of moment arm on angle (a static gear shift)
by using multi-bar transmissions,
or by using tendon attachments with antagonistic actuators.
Note that the actuators do not need to be symmetric.
Gear shifts and variable transmissions would allow the maximum torque
and maximum no-load speed of the joint to be increased (also true
for all other actuation types).
